Market Simulator

### 2020-08-05 analysis/05_market_simulator.Rmd
Reorganized the layout made only one set of tabs of each organizations with personas, org inputs, and gauges

<!-- Persona 1 page -->

Persona 1 (change this to Org 1) {.tabset .tabset-fade}
--------------------------------------------------

### Market Share Chart Persona 1
<!-- Might get rid of this graph -->

```{r plot person 1}
renderPlotly({
  choice = df()
  persona = p_beta1 # Choose the persona

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
  df <- as.data.frame(matrix(data, 8, 1))

  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8)
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Organization)) +
             geom_col() +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none") +
             facet_wrap(~Type)
    )
})
```

### Amnesty International Market Share

```{r valuebox ai persona 1}
renderValueBox({
  choice = df()

@@

@@

```{r valuebox gp persona 1}
renderValueBox({
  choice = df()
  persona = p_beta1 # Choose the persona

@@

@@

```{r valuebox ox persona 1}
renderValueBox({
  choice = df()

@@

@@

```{r valuebox rc persona 1}
renderValueBox({
  choice = df()

@@

Organizations {.tabset .tabset-fade}
-------------------------------------
### Amnesty International

```{r echo=FALSE}
selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

```{r echo=FALSE}
renderGauge({
  choice = df()
  persona = p_beta1 # Choose the persona

### Greenpeace

```{r echo=FALSE}
selectInput("gp_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

### Oxfam

```{r echo=FALSE}
selectInput("ox_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

### Red Cross

```{r echo=FALSE}
selectInput("rc_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

@@

@@

Persona 2 {.tabset .tabset-fade}
--------------------------------------------------

### Market Share Persona 2

```{r plot persona 2}
renderPlotly({
  choice = df()

  persona = p_beta2 # Choose the persona

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
  df <- as.data.frame(matrix(data, 8, 1))

  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8)
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Organization)) +
             geom_col() +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none") +
             facet_wrap(~Type)
    )
})
```

### Amnesty International Market Share

```{r valuebox ai persona 2}
renderValueBox({
  choice = df()

  persona = p_beta2 # Choose the persona

```{r valuebox gp persona 2}
renderValueBox({
  choice = df()

  persona = p_beta2 # Choose the persona

```{r valuebox ox persona 2}
renderValueBox({
  choice = df()

  persona = p_beta2 # Choose the persona

```{r valuebox rc persona 2}
renderValueBox({
  choice = df()

  persona = p_beta2 # Choose the persona

Organizational Inputs {.tabset .tabset-fade}
-------------------------------------
### Amnesty International Inputs

```{r echo=FALSE}
selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

### Greenpeace Inputs

```{r echo=FALSE}
selectInput("gp_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

### Oxfam Inputs

```{r echo=FALSE}
selectInput("ox_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

### Red Cross Inputs

```{r echo=FALSE}
selectInput("rc_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

@@

Persona 3 {.tabset .tabset-fade}
--------------------------------------------------

### Market Share Persona 3
```{r plot persona 3}
renderPlotly({
  choice = df()

  persona = p_beta3 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
  df <- as.data.frame(matrix(data, 8, 1))

  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8)
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Organization)) +
             geom_col() +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none") +
             facet_wrap(~Type)
    )
})
```

### Amnesty International Market Share

```{r valuebox ai persona 3}
renderValueBox({
  choice = df()

  persona = p_beta3 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)

```{r valuebox gp persona 3}
renderValueBox({
  choice = df()

  persona = p_beta3 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)

```{r valuebox ox persona 3}
renderValueBox({
  choice = df()

  persona = p_beta3 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)

```{r valuebox rc persona 3}
renderValueBox({
  choice = df()

  persona = p_beta3 # Choose the persona

  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2)

Organizational Inputs {.tabset .tabset-fade}
-------------------------------------
### Amnesty International Inputs

```{r echo=FALSE}
selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

### Greenpeace Inputs

```{r echo=FALSE}
selectInput("gp_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

### Oxfam Inputs

```{r echo=FALSE}
selectInput("ox_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

### Red Cross Inputs

```{r echo=FALSE}
selectInput("rc_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

@@

Expected Donors {.tabset .tabset-fade}
-------------------------------------
### Amnesty International Expected Donors

```{r echo=FALSE}
renderGauge({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(public_political_social_charity_demo[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(public_political_social_charity_demo[,2])),2)

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})
```

>>>>

<!-- Organizational Tabs -->

Organization Breakdown {.tabset .tabset-fade}
--------------------------------------------------
### Amnesty International Market Share

```{r plot ai plot}
renderPlotly({
  choice = df()

  data <- c(ai_exp_util1, ai_rate1, 
            ai_exp_util2, ai_rate2,
            ai_exp_util3, ai_rate3)

  df <- as.data.frame(matrix(data, 6, 1))

  df[,2] <- c("Amnesty International")
  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

```{r valuebox ai}
renderValueBox({
  choice = df()

@@

```{r ai org inputs}
selectInput("ai_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

```{r ai gauge}
renderGauge({
  choice = df()
  persona = p_beta1 # Choose the persona

@@

```{r plot gp plot}
renderPlotly({
  choice = df()

  data <- c(gp_exp_util1, gp_rate1, 
            gp_exp_util2, gp_rate2,
            gp_exp_util3, gp_rate3)

  df <- as.data.frame(matrix(data, 6, 1))

  df[,2] <- c("Greenpeace")
  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

```{r valuebox gp}
renderValueBox({
  choice = df()
  persona = p_beta1 # Choose the persona

@@

```{r gp org inputs}
selectInput("gp_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

```{r gp gauge}
renderGauge({
  choice = df()
  persona = p_beta1 # Choose the persona

  gauge(gp_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})
```

@@

```{r plot ox plot}
renderPlotly({
  choice = df()

  data <- c(ox_exp_util1, ox_rate1, 
            ox_exp_util2, ox_rate2,
            ox_exp_util3, ox_rate3)

  df <- as.data.frame(matrix(data, 6, 1))

  df[,2] <- c("Oxfam")
  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

```{r valuebox ox}
renderValueBox({
  choice = df()

@@

```{r ox org inputs}
selectInput("ox_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

```{r ox gauge}
renderGauge({
  choice = df()
  persona = p_beta1 # Choose the persona

  gauge(ox_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})
```

@@

```{r plot rc plot}
renderPlotly({
  choice = df()

  data <- c(rc_exp_util1, rc_rate1, 
            rc_exp_util2, rc_rate2,
            rc_exp_util3, rc_rate3)

  df <- as.data.frame(matrix(data, 6, 1))

  df[,2] <- c("Red Cross")
  df[,3] <- rep(c("Utility", "Market Share"), length.out = 6)
  df[,4] <- c(rep("Persona 1", 2),rep("Persona 2", 2), rep("Persona 3", 2))
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

```{r valuebox rc}
renderValueBox({
  choice = df()

@@

```{r rc org inputs}
selectInput("rc_issue", 
            label = "Select Issue Area:",
            choices = c("Emergency response",
                        "Environment",
                        "Human rights",
                        "Refugee relief"))

@@

```{r rc gauge}
renderGauge({
  choice = df()
  persona = p_beta1 # Choose the persona

  gauge(rc_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#660000"),
        symbol = "%")
})
```

@@

<!-- Persona 2 {.tabset .tabset-fade} -->
<!-- -------------------------------------------------- -->

<!-- ### Market Share Persona 2 -->

<!-- ```{r plot persona 2} -->
<!-- renderPlotly({ -->
<!--   choice = df() -->

<!--   persona = p_beta2 # Choose the persona -->

<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->

<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->

<!--   data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate) -->
<!--   df <- as.data.frame(matrix(data, 8, 1)) -->

<!--   df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross") -->
<!--   df[,3] <- c(rep("Utility", 4), rep("Market Share", 4)) -->
<!--   df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8) -->
<!--   colnames(df) <- c('Value', 'Organization', "Type", "Persona") -->

<!--   ggplotly(df %>% filter(Type == "Market Share") %>%  -->
<!--              ggplot(aes(y = Value, x = Organization, fill = Organization)) + -->
<!--              geom_col() + -->
<!--              labs(x="") +  -->
<!--              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) + -->
<!--              theme(legend.position = "none") + -->
<!--              facet_wrap(~Type) -->
<!--     ) -->
<!-- }) -->
<!-- ``` -->

<!-- ### Amnesty International Market Share -->

<!-- ```{r valuebox ai persona 2} -->
<!-- renderValueBox({ -->
<!--   choice = df() -->

<!--   persona = p_beta2 # Choose the persona -->

<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->

<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->

<!--   valueBox(ai_rate, -->
<!--            color = "#FFC30B", -->
<!--            icon = "fa-percent") -->
<!-- }) -->
<!-- ``` -->

<!-- ### Greenpeace Market Share -->

<!-- ```{r valuebox gp persona 2} -->
<!-- renderValueBox({ -->
<!--   choice = df() -->

<!--   persona = p_beta2 # Choose the persona -->

<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->

<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->

<!--   valueBox(gp_rate, -->
<!--            color = "#3fad48", -->
<!--            icon = "fa-percent") -->
<!-- }) -->
<!-- ``` -->

<!-- ### Oxfam Market Share -->

<!-- ```{r valuebox ox persona 2} -->
<!-- renderValueBox({ -->
<!--   choice = df() -->

<!--   persona = p_beta2 # Choose the persona -->

<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->

<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->

<!--   valueBox(ox_rate, -->
<!--            color = "#006633", -->
<!--            icon = "fa-percent") -->
<!-- }) -->
<!-- ``` -->

<!-- ### Redcross Market Share -->

<!-- ```{r valuebox rc persona 2} -->
<!-- renderValueBox({ -->
<!--   choice = df() -->

<!--   persona = p_beta2 # Choose the persona -->

<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona)),2) -->
<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona)),2) -->
<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona)),2) -->
<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona)),2) -->

<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->

<!--   valueBox(rc_rate, -->
<!--            color = "#660000", -->
<!--            icon = "fa-percent") -->
<!-- }) -->
<!-- ``` -->

@@

<!-- Persona 3 {.tabset .tabset-fade} -->
<!-- -------------------------------------------------- -->

<!-- ### Market Share Persona 3 -->
<!-- ```{r plot persona 3} -->
<!-- renderPlotly({ -->
<!--   choice = df() -->

<!--   persona = p_beta3 # Choose the persona -->

<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->

<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->

<!--   data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate) -->
<!--   df <- as.data.frame(matrix(data, 8, 1)) -->

<!--   df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross") -->
<!--   df[,3] <- c(rep("Utility", 4), rep("Market Share", 4)) -->
<!--   df[,4] <- rep(c("Persona 1","Persona 2", "Persona 3"), length.out = 8) -->
<!--   colnames(df) <- c('Value', 'Organization', "Type", "Persona") -->

<!--   ggplotly(df %>% filter(Type == "Market Share") %>%  -->
<!--              ggplot(aes(y = Value, x = Organization, fill = Organization)) + -->
<!--              geom_col() + -->
<!--              labs(x="") +  -->
<!--              scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) + -->
<!--              theme(legend.position = "none") + -->
<!--              facet_wrap(~Type) -->
<!--     ) -->
<!-- }) -->
<!-- ``` -->

<!-- ### Amnesty International Market Share -->

<!-- ```{r valuebox ai persona 3} -->
<!-- renderValueBox({ -->
<!--   choice = df() -->

<!--   persona = p_beta3 # Choose the persona -->

<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->

<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->

<!--   valueBox(ai_rate, -->
<!--            color = "#FFC30B", -->
<!--            icon = "fa-percent") -->
<!-- }) -->
<!-- ``` -->

<!-- ### Greenpeace Market Share -->

<!-- ```{r valuebox gp persona 3} -->
<!-- renderValueBox({ -->
<!--   choice = df() -->

<!--   persona = p_beta3 # Choose the persona -->

<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->

<!--   gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->

<!--   valueBox(gp_rate, -->
<!--            color = "#3fad48", -->
<!--            icon = "fa-percent") -->
<!-- }) -->
<!-- ``` -->

<!-- ### Oxfam Market Share -->

<!-- ```{r valuebox ox persona 3} -->
<!-- renderValueBox({ -->
<!--   choice = df() -->

<!--   persona = p_beta3 # Choose the persona -->

<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->

<!--   ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->

<!--   valueBox(ox_rate, -->
<!--            color = "#006633", -->
<!--            icon = "fa-percent") -->
<!-- }) -->
<!-- ``` -->

<!-- ### Redcross Market Share -->

<!-- ```{r valuebox rc persona 3} -->
<!-- renderValueBox({ -->
<!--   choice = df() -->

<!--   persona = p_beta3 # Choose the persona -->

<!--   ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(persona[,1])),2) -->
<!--   gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(persona[,1])),2) -->
<!--   ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(persona[,1])),2) -->
<!--   rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(persona[,1])),2) -->

<!--   rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->

<!--   valueBox(rc_rate, -->
<!--            color = "#660000", -->
<!--            icon = "fa-percent") -->
<!-- }) -->
<!-- ``` -->

@@

<!-- Expected Donors {.tabset .tabset-fade} -->
<!-- ------------------------------------- -->
<!-- ### Amnesty International Expected Donors -->

<!--   ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util)) -->
<!--   gauge(ai_rate, -->
<!--         min = 0, -->
<!--         max = 100, -->
<!--         gaugeSectors(colors = "#FFC30B"), -->
<!--         symbol = "%") -->
<!-- }) -->
<!-- ``` -->
